%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rujhanarora/}{\Large Rujhan Arora}} & Email : \href{mailto:rujhanarora.96@gmail.com}{rujhanarora.96@gmail.com}\\
  \href{https://www.linkedin.com/in/rujhanarora/}{{https://www.linkedin.com/in/rujhanarora/}} & Mobile : 8571086069 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology(NIT), Kurukshetra}{Kurukshetra, Haryana}
      {B.Tech in Computer Science;  CGPA: 8.4}{July. 2013 -- May. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Fastfox.com}{Gurgaon, Haryana}
      {Software Development Engineer}{Oct 2018 - Present}
      \resumeItemListStart
      \resumeItem{Fastfox Agents}
            {Implemented a new flexible Incentive System in backend for Fastfox Agents' incentives (Monthly, Quarterly etc), alongwith various other Rubackend API's for the app. Fastfox Agents is an android and ios app for fastfox brokers.}
        \resumeItem{BroEx}
          {Revamped BroEx feed for the users. Also, implemented various backend API's for the app. BroEx is the largest network of Real Estate Brokers in India having features like News Feed, Auto Match Notification, Property view and search etc.}
        \resumeItem{Internal Admin Panel}
          {Implemented various API's for internal panel for Fastfox employees of various roles. Admin panel is a web panel for internal employees for all their designated tasks.}
        \resumeItem{Fastfox}
          {Fastfox is an online platform to get properties on rental basis.}
        \resumeItem{Tech Stack:}
          {Node.js, PostgreSQL, Redis, RabbitMQ}
      \resumeItemListEnd

    \resumeSubheading
      {Fidelity Investments}{Chennai, Tamil Nadu}
      {Software Engineer}{Aug 2017 - Sep 2018}
      \resumeItemListStart
        \resumeItem{Reference Point- FI and WI Discretionary}
          {Worked as a part of Reference Point- FI and WI Discretionary, which is a cloud hosted application(MS sharepoint) storing different plan details in the form of topics, maps and content requests at different levels.}
        \resumeItem{Scrum Bot (BU Project)}
          {Developed Scrum Bot for Agile Teams, which takes input from user through Skype and performs various functions in JIRA board. Rather than going to JIRA website, users can directly type in queries in Skype input itself to get desired results.}
        \resumeItem{Buy Local Bond CMS System (Training Project)}
          {Developed end-to-end client management system, a Web application to manage and record all activities and preference details of clients under authorized brokers, using JAVA, Angular 4 and MySQL.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Classification of Trash Based On Recyclability Status (Jan, 2017 – Apr, 2017)}
      {Developed a project (achieving 88\% accuracy), whose objective was to take images of a single piece of garbage and classify it into five classes- glass, leather, paper, plastic and metal using Computer Vision(CV) approach and Machine Learning, using Python. Used SIFT for feature extraction, K-means clustering for grouping and SVM for classification)}
    \resumeSubItem{Student and Teacher Attendance Manager}
      {Developed an android app for taking attendance of both students (by teachers) and teachers (By Admins). Used JAVA and XML with SQLite as database.}
  \resumeSubHeadingListEnd
  
  %-----------PROJECTS-----------------
\section{Achievements and Responsibilities}
  \resumeSubHeadingListStart
    \resumeSubItem{Global Leaderboard rank – 87 @ {\href{https://www.interviewbit.com}{InterviewBit}} }
      {Profile -{\href{https://www.interviewbit.com/profile/slrparser}{https://www.interviewbit.com/profile/slrparser}} {\href{https://www.interviewbit.com}{InterviewBit}} is a reputed website to test your Data Structures, Algorithms and Coding Skills. I am currently ranked 87 globally, among a pool of more than 2.5 lakh users}
    \resumeSubItem {1st position}
      {In Blindcoding , TechSpardha(College Technical Fest) (10/2014 – 10/2014). Blindcoding is an annual event where programming questions have to be solved, with computer screen getting turned off every 5 minutes.}
    \resumeSubItem {1st position}
      {In Humbug , TechSpardha(College Technical Fest) (10/2014 – 10/2014). Humbug is an annual event where programming questions have to be solved in a section and bugs have to found out from a given code, in other section}
    \resumeSubItem {AIR 5934} {In JEE–Mains (05/2013 – 06/2013)}
    \resumeSubItem {AIR 9400} {In JEE–Advanced (05/2013 – 06/2013)}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Proficient}{: Node.js, Javascript, Data Structures and Algorithms, PostgreSQL }
    }
    \item{
     \textbf{Comfortable}{: Redis, C++, JAVA, HTML, jQuery}
    }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

